---
title: "Package Knapsack"
author: "Obaid Ur Rehman,Muhammad Habib"
date: "October 2, 2018"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
  html_document:  
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

A Package to solve knapsack problem using 3 different algorhitms.

## Kanpsack Problem ?
The knapsack problem is a discrete optimization problem where we have a knapsack that can take a limited **weight W** and we want to fill this knapsack with a   **number of items i = 1, ..., n,**  each with a **weight wi** and a **value vi**
.The goal is to find the knapsack with the largest value of the elements added to the knapsack.This problem is `NP-hard, meaning that it is ”at least as hardas the hardest problem in NP”`
ref: ([via](https://en.wikipedia.org/wiki/NP-hardness))


## Three Different algorithms to solve a knapsack problem?
- brute force knapsack **brute force knapsack(x,W, parallel  = FALSE)**
- knapsack dynamic      **knapsack_dynamic(x,W)**   
- greedy knapsack       **greedy_knapsack(x,W)**


##Arugments 

- **x** is data frame which has **w** as weight column and **v** as value of each weight item
- **W** captial **W** is represent a knapscak capcaity that knapsack can carry
- **parallel** which is only used in brute force search alogrithm if you want to run on mulitple core than set is as **TRUE**. The default value is set as **FALSE**

##generate a data

```{r}
library(knapsack)
set.seed(345) 
n <- 3000   
knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE),
                                v=runif(n = n, 0, 10000)
)

head(knapsack_objects) 
```

## brute_force_knapsack(x,W)


```{r, warning= FALSE, message= FALSE}
brute_force_knapsack(knapsack_objects[1:8,], W = 3500)
```

```{r, warning= FALSE, message= FALSE}
brute_force_knapsack(x = knapsack_objects[1:12,], W = 2000)
```

## How much time does it takes to run the algorithm for n = 16 objects?

```{r}

set.seed(42) 
n <- 16  
knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE),
                                v=runif(n = n, 0, 10000))

system.time(brute_force <- brute_force_knapsack(x = knapsack_objects[1:12,], W = 2000))
```


## knapsack_dynamic(x, W)

```{r, warning= FALSE, message= FALSE}
knapsack_dynamic(knapsack_objects[1:8,], W = 3500)
```

```{r, warning= FALSE, message= FALSE}
knapsack_dynamic(x = knapsack_objects[1:12,], W = 2000)
```

## How much time does it takes to run the algorithm for n = 500 objects?

```{r}

set.seed(42)
n <- 500
knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE),
                                v=runif(n = n, 0, 10000))
system.time(dynamic_result<- knapsack_dynamic(x = knapsack_objects[1:12,], W = 2000))
```



## greedy_knapsack(x, W)

```{r, warning= FALSE, message= FALSE}
greedy_knapsack(knapsack_objects[1:800,], W = 3500)
```

```{r, warning= FALSE, message= FALSE}
greedy_knapsack(x = knapsack_objects[1:12,], W = 2000)
```

## How much time does it takes to run the algorithm for n = 1000000 objects?

```{r}
set.seed(42) 
n <- 1000000  
knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE),
                                v=runif(n = n, 0, 10000))
system.time(greedy_result <- greedy_knapsack(x = knapsack_objects[1:12,], W = 2000))
```

## Parallelize brute force search
The brute force algorithm is straight forward to parallelize for computers with multiple cores. we have Implement an argument parallel in brute force knapsack() that is FALSE by default.` If set to TRUE, the function should parallelize
over the detected cores`.



## Microbenchmark package to compare how long each variation takes to run

```{r, echo=TRUE}
library(microbenchmark)

microbenchmark(
  "brute_force"= brute_force, #n= 16
  "dynamic_knapsack" = dynamic_result, #n= 500
  "greedy" = greedy_result ,#n = 1000000
  times = 1,
  unit = "us"
)
```

### Note!
Its is platform dependent and only work with `MacOS/Linux or Windows`.


